BIP Architectures and Open pNets

### 2019-01-28 2018-Arch-pNets/arch-pNets.tex
arch-pNets paper: Updated the encoding to include primed variables and update expressions

\begin{example}[An open-transition]
  \label{OT:enable-composed}
  The \texttt{Failure TimerMonitor} pNet of \Fig{FailureTimer:pNet} has \replaceSB{2 controllers 
  and 2 holes. O}{two coordinators and four dangling ports, which can be grouped into two holes (see \secn{encoding} below).  Disregarding the maximal progress priority, o}ne of its possible open-transitions is:\\[-2ex]
%%   \footnote{Note the underlined action notation that we use to represent synchronised actions, i.e. actions that are the result of a synchronisation and that we declare as \emph{non-observable}. Those actions are only used for monitoring purposes and statement of properties but cannot be synchronised again in a synchronisation vector. This allows us to define a weak bisimilarity equivalence with p=compositional properties.}
%%   : 
%% \noteLH{underline notation might be a bit too much for this paper : see at the end if we remove it or not (will we use it?)}
% \smallskip
%$  OT_1  = \openrule
%{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
%{\ostate{00} \OTarrow{\underline{\alpha_4}} \ostate{11}}
%$
%\medskip
\begin{small}\[ \openrule
  {\{B\mapsto fail(b0)\},\\
    t<GetMax(z) \land b1=true \land b1=>b0 \land z1= (z \cap (b1?zone;TopInt)+t),
    \{z:=z1\} }
  {\ostate{11} \OTarrow{\alpha_0} \ostate{12}}
  \]
\end{small}\vspace{-1.5ex}
%
%The first one, $OT_1$, corresponds to the simultaneous initialisation
%of both controlers. No hole is active at that time, and the resulting
%global action is denoted $\alpha_4$.

@@

\paragraph{Encoding the coordinators}
To encode a coordinator $C$, we 1)~introduce a fresh initial state with an additional
$\init$ transition that initialises all the variables to those defined
by the initial valuation $\val{0}{C}$ of $C$, 2)~define a pNet action algebra that associates, as action parameter, an
additional Boolean value to each port, 3)~create pNet transitions that reflect the original transitions of
$C$ with $\true$ as parameter and 4)~create additional loop transitions marked by
$\false$.

Formally,  $\nopri[C] \bydef{=} \pNetTuple{S, s_0, \goesto[{\nopri[C]}]{}}$, such that
%
\begin{itemize}
\item $s_0 \not\in Q_C$ is fresh and $S = Q_C \cup \{s_0\}$,
\item $\vars(s) = V_C$, for all $s \in Q_C$, and $\vars(s_0) =
  \emptyset$,
%% \item the transition relation $\goesto[{\nopri[C]}]{}$ is defined as
%%   the union of three sets of transitions
%%   (with $\mathit{init} \bydef{=} \bigl(x := \val{0}{C}(x)\bigr)^{x \in V_C}$):
%% %
%%   \begin{multline}
%%     \label{eq:nopri:trans}
%%     {\goesto[{\nopri[C]}]{}} \bydef{=}
%%     \bsetdef{\tuple{s, a(\true), g, u, s'}}{
%%       \tuple{s, a, g, u, s'} \in \goesto{}}
%%     \\    
%%     \cup
%%     \bsetdef{\tuple{s, a(\false), \true, \noop, s}}{
%%       s \in Q_C, a \in P_C}
%%     %% \\
%%     \cup
%%     \bigl\{(s_0, \init, \true, \mathit{init}, q^0_C)\bigr\}
%%     \,.
%%   \end{multline}

\item ${\goesto[{\nopri[C]}]{}} \bydef{=} T_1 \cup T_2 \cup T_3$, with
  $T_1 = \bsetdef{\tuple{s, a(\true), g, u, s'}}{
      \tuple{s, a, g, u, s'} \in \goesto{}}$,
  $T_2 = \bsetdef{\tuple{s, a(\false), \true, \noop, s}}{
      s \in Q_C, a \in P_C}$,
  $T_3 = \bigl\{(s_0, \init, \true, \mathit{init}, q^0_C)\bigr\}$
    and $\mathit{init} \bydef{=} \bigl(x := \val{0}{C}(x)\bigr)^{x \in V_C}$.
\end{itemize}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.9\columnwidth]{FailureTimerPNET-v4}
  \caption{The open pNET encoding the Failure Monitor architecture (\fig{schema:ArchFailure:BIP}) without the priority model}
  \label{fig:FailureTimer:pNet}
\end{figure}

@@

The encoding of the interaction model is based on its representation
as a set of connectors. \noteSB{%
%
  A legitimate question is whether we actually need to do this,
  instead of listing explicitly the individual interactions, then
  associating a synchronisation vector to each one of them?  One of
  the factors is the encoding pNets$\rightarrow$SAT: is it better to
  have more or fewer SVs if the price is additional Boolean variables?
  The other factor might be the facility of maximal progress
  encoding\mdash TBC.  Traceability.  Anything else?
%
} Indeed, as illustrated by the Failure Monitor architecture in
\fig{schema:ArchFailure:BIP}, each connector can define several
allowed interactions, depending on its hierarchical structure and the
use of synchrons and triggers.

In order to encode these interactions using only one synchronisation vector, we use
the additional Boolean values associated to each port by the encoding
of coordinator components.  We observe that the three ports in this
connector form a ``causality chain'': {\NameCtrl.\PortFail} can only
participate in the interaction if the dangling port {\PortFail}
participates, which in turn can only participate if
{\NameTimer.\PortTick} does so.  These dependencies can be rewritten
as Boolean implications $\NameCtrl.\PortFail \Rightarrow \PortFail$
and $\PortFail \Rightarrow \NameTimer.\PortTick$.
%
The conjunction of these two implications can be used as a guard for
the synchronisation vector encoding connector {\NameTimer.\PortTick
  \trigsynch (\PortFail \trigsynch \NameCtrl.\PortFail)}.

@@

We obtain the
synchronisation vector SV0 shown in \fig{FailureTimer:pNet}, where $b_0$ and
$b_1$ are the Boolean values associated to the actions encoding the
ports {\PortFail} and {\NameCtrl.\PortFail}, $\alpha_0$ is a fresh
action name.  The guard $b_1 \Rightarrow b_0$ encodes the causal
relation among ports {\NameCtrl.\PortFail} and {\PortFail}.  Notice
that, in our encoding, all three ports are present in the
synchronisation vector.  \Fig{FailureTimer:pNet} shows
the four synchronisation vectors SV0\ndash SV3 corresponding to the
connectors in \fig{schema:ArchFailure:BIP} and an additional vector
SV4, synchronising the {\init} transitions of the two pLTSs.

The general case encoding relies on the causal semantics of the
algebra of BIP connectors \cite{BliSif10-causal-fmsd}.  Disregarding
the variables and data transfer, the Algebra of Connectors $\ac(P)$
\cite{BliSif07-acp-emsoft} provides a syntactic notation for the BIP
connectors.  The causal semantics of the connectors, given in terms of
the Algebra of Causal Interaction Trees $\ct(P)$, explicitates the
causal dependencies discussed above, through an encoding mapping
$\tau: \ac(P) \rightarrow \ct(P)$.  Another mapping $R: \ct(P)
\rightarrow \cru(P)$ encodes causal interaction trees into systems of
causal rules, which are Boolean implications similar to the ones in
the example above.  We briefly summarise the key definitions and
results in \app{algebras}.  The $\ac(P)$, $\ct(P)$ and $\cru(P)$
representations of the connectors in \fig{schema:ArchFailure:BIP} are
shown in \tab{connectors}.

@@

Below, we assume that, as in \fig{schema:ArchFailure:BIP}, the
interaction model is defined by a set of connectors, annotated with
Boolean guards and with update assignments.  In particular, we assume
that the guards and update assignments are well-defined for any
interaction allowed by the connector.  For example, the choice
$\NameCtrl.\PortFail\ ?\ \NameCtrl.\mathit{zone} : \topinterval$ in
the update assignement
\[
\NameTimer.\mathit{z} := \NameTimer.\mathit{z}
\cap \Big(
\bigl(
\NameCtrl.\PortFail\ ?\ \NameCtrl.\mathit{zone} : \topinterval
\bigr)
+ \NameTimer.\mathit{t} \Big)
\]
associated to the connector {\NameTimer.\PortTick \trigsynch
  (\PortFail \trigsynch \NameCtrl.\PortFail)} in
\fig{schema:ArchFailure:BIP} ensures that the assignment is
well-defined independently of whether {\NameCtrl.\PortFail}
participates or not.  Let us denote by $\gamma \subset \ac(P_A)
\times \guards{V_A} \times \assigns{V_A}$ the set of connectors in the
architecture $A$ and by $P_x$ the set of ports involved in the
connector $x \in \gamma$.  Then, we have
\begin{align*}
  \gamma &=
  \setdef{(x, g, u)}{x \in \ac(P_x), g \in \guards{V_x}, u \in
    \assigns{V_x}}
  \\
  &\simeq \setdef{(a,g,u)}{(x,g,u) \in \gamma, a \in \intsem{x}}
  = \Gamma
  \,.
\end{align*}

We first define the encoding of $\Gamma$ as $\nopri[\Gamma] \bydef{=}
\setdef{\nopri[x,g,u]}{(x,g,u) \in \gamma}$, where $\nopri[x,g,u]$ is the synchronisation vector defined by
%
\begin{equation}
  \label{eq:nopri:connector}
  \nopri[x,g,u] \bydef{=}
  \bigl(p(b_p,\export[A](p))\bigr)^{p \in P_x}
  \rightarrow
  \alpha_p
  \left[\bigwedge R(\tau(x))\bigl[\nicefrac{b_p}{p}\bigr]\right]
  \,,
\end{equation}
%
with $b_p$ a fresh Boolean variable, $\alpha_p$ a fresh name, $\tau :
\ac(P_A) \rightarrow \ct(P_A)$ and $R : \ct(P_A) \rightarrow
\cru(P_A)$ the two mappings defined in \app{transformations} and
illustrated in \tab{connectors}, $\bigl[\nicefrac{b_p}{p}\bigr]$ is
the substitution, which replaces, in the expression that preceeds it,
all occurrences of $p$ by $b_p$.

\todoLHin{The update assignment is missing from the above encoding.
  It should be $u\bigl[\nicefrac{b_p}{p}\bigr]$, but I do not see in
  \defn{pnets} where should I place it.  I think it is missing there.
  \Simon}

\begin{theorem}
  The open automaton $\semopen{\nopri[A,\partition]}$ corresponding to
  $\nopri[A,\partition]$ (see \defn{operationalSemantics}) is
  isomorphic to the LTS $\semopen{\Gamma\bigl(\cC_A, (B_D)^{D \in
      \partition}\bigr)}$ (see \defn{comp:semantics}), where, for each
  $D \in \partition$, the component $B_D \bydef{=} \tuple{\{q\}, q,
    V_D, \val{0}{D}, D, \export[D], \goesto{}}$, with
%
  \begin{align*}
    V_D &= \bigcup_{p \in D} \export[A](p)
    \,,
    &\val{0}{D}(v) &= \bot, \text{ for all $v \in V_D$}
    \,,\\
    \goesto{} &= \bsetdef{(q, p, \true, \noop, q)}{p \in D}
    \,,
    &\export[D](p) &= \export[A](p), \text{ for all $p \in D$}
    \,,
  \end{align*}
%
  and $q$ a fresh state.
\end{theorem}
%
\begin{proof}[Sketch of a proof]
  The theorem follows from the correctness of $\tau$ and $R$ shown in
  \cite{BliSif10-causal-fmsd}.
\end{proof}

\noteSBin{This theorem is very probably correct: the key question is
  whether isomorphism is, indeed, the relation to use. In absence of
  silent transitions, must be the case.}

Observe now that this encoding can be optimised to remove unnecessary
Boolean variables and loop transitions marked by \false.  For
instance, consider the ports shown in red in the second column of
\tab{connectors}.  All these ports only appear in the roots of the
corresponding causal interaction trees and, furthermore, each of these
trees only has one root (see \app{trees}).  In such cases, as in the
{\NameTimer.\PortTick \trigsynch (\PortFail \trigsynch
  \NameCtrl.\PortFail)} example discussed above, the Boolean variables
and the \false-marked loop transitions associated to these ports can
be removed.  Furthermore, the rules associated to these ports in the
corresponding systems of causal rules (see the rules in red in the
third column of \tab{connectors}) become tautological and can also be
removed from the corresponding guards in \eq{nopri:connector}.

@@

>>>>

\begin{example}[An open-transition]
  \label{OT:enable-composed}
  The \texttt{Failure TimerMonitor} pNet of \Fig{FailureTimer:pNet} has \replaceSB{2 controllers 
  and 2 holes. O}{two coordinators and four dangling ports, which can be grouped into two holes (see \secn{encoding} below).  Disregarding the maximal progress priority, o}ne of its possible open-transitions is:\\[-2ex]
%%   \footnote{Note the underlined action notation that we use to represent synchronised actions, i.e. actions that are the result of a synchronisation and that we declare as \emph{non-observable}. Those actions are only used for monitoring purposes and statement of properties but cannot be synchronised again in a synchronisation vector. This allows us to define a weak bisimilarity equivalence with p=compositional properties.}
%%   : 
%% \noteLH{underline notation might be a bit too much for this paper : see at the end if we remove it or not (will we use it?)}
% \smallskip
%$  OT_1  = \openrule
%{\emptyset, \{t:=0, z:=TopInt, zone:=[minZone,maxZone]\} }
%{\ostate{00} \OTarrow{\underline{\alpha_4}} \ostate{11}}
%$
%\medskip
\begin{small}\[ \openrule
  {\{B\mapsto fail(b0)\},\\
    t<GetMax(z) \land b1=true \land b1=>b0 \land z'= (z \cap (b1?zone;TopInt)+t) {\color{blue}\land (t' = t) \land (zone' = zone)},\\
    \{z:=z', {\color{blue}t := t'+1, zone := zone'}\} }
  {\ostate{11} \OTarrow{\alpha_0} \ostate{12}}
  \]
\end{small}\vspace{-1.5ex}
%
%The first one, $OT_1$, corresponds to the simultaneous initialisation
%of both controlers. No hole is active at that time, and the resulting
%global action is denoted $\alpha_4$.

@@

\paragraph{Encoding the coordinators}
To encode a coordinator $C$, we 1)~introduce a fresh initial state with an additional
$\init$ transition that initialises all the variables to those defined
by the initial valuation $\val{0}{C}$ of $C$, 2)~define a pNet action algebra that associates, as action parameter, an
additional Boolean value to each port, \add{3)~for each exported variable $x$, create the corresponding fresh variable $x'$ to allow updates during interactions,} 4)~create pNet transitions that reflect the original transitions of
$C$ with $\true$ as parameter and 5)~create additional loop transitions marked by
$\false$.

Formally,  $\nopri[C] \bydef{=} \pNetTuple{S, s_0, \goesto[{\nopri[C]}]{}}$, such that
%
\begin{itemize}
\item $s_0 \not\in Q_C$ is fresh and $S = Q_C \cup \{s_0\}$,
\item $\vars(s) = V_C \cup \setdef{x'}{x \in \export[C](p), p \in a, s\goesto{a} }$, for all $s \in Q_C$, and $\vars(s_0) =
  \emptyset$,
%% \item the transition relation $\goesto[{\nopri[C]}]{}$ is defined as
%%   the union of three sets of transitions
%%   (with $\mathit{init} \bydef{=} \bigl(x := \val{0}{C}(x)\bigr)^{x \in V_C}$):
%% %
%%   \begin{multline}
%%     \label{eq:nopri:trans}
%%     {\goesto[{\nopri[C]}]{}} \bydef{=}
%%     \bsetdef{\tuple{s, a(\true), g, u, s'}}{
%%       \tuple{s, a, g, u, s'} \in \goesto{}}
%%     \\    
%%     \cup
%%     \bsetdef{\tuple{s, a(\false), \true, \noop, s}}{
%%       s \in Q_C, a \in P_C}
%%     %% \\
%%     \cup
%%     \bigl\{(s_0, \init, \true, \mathit{init}, q^0_C)\bigr\}
%%     \,.
%%   \end{multline}

\item denoting  $\mathit{init} \bydef{=} \bigl(x := \val{0}{C}(x)\bigr)^{x \in V_C}$;
  \noteSB{Ludo, Eric, pourriez-vous v\'erifier que cela est compr\'ehensible ?}%
  \add{for $s \goesto{a, g, u} s'$ with $u = (x := e_x)^{x
    \in V}$ (for some $V \subseteq V_C$),
%  
  $u' \bydef{=}
  \bigl(x := e_x\bigr)^{x \in V \setminus \export[C](a)}
  \cup
  \bigl(x := e_x\bigl[\nicefrac{x'}{x}\bigr]\bigr)^{x \in V \cap \export[C](a)}$,
%
  and $\export[C]'(a) \bydef{=} \setdef{x'}{x \in \export[C](p), p \in a}$,
%
  \begin{multline*}
    {\goesto[{\nopri[C]}]{}} \bydef{=} 
    \Setdef{\Tuple{s, a\bigl(\export[C](a), \export[C]'(a),\true\bigr), g, u', s'}}{
      s \goesto{a, g, u} s'}
    \\
    {} \cup
    \Setdef{\Tuple{s, a\bigl(\export[C](a), \export[C]'(a),\false\bigr), \true, \noop, s}}{
      s \in Q_C, \exists s' \in Q_C: s' \goesto{a}}
    \\
    {} \cup \bigl\{(s_0, \init, \true, \mathit{init}, q^0_C)\bigr\}.
  \end{multline*}}
\end{itemize}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=0.9\columnwidth]{FailureTimerPNET-v4}
  \caption{The open pNET encoding the Failure Monitor architecture (\fig{schema:ArchFailure:BIP}) without the priority model}
  \label{fig:FailureTimer:pNet}
%
  \noteSBin{The updated encoding exports more primed variables in the
    actions, \eg $tick(z,t,z',t')$ and $fail(zone, zone', b1)$ instead
    of $tick(z,t,z')$ and $fail(zone, b1)$, and SVs, \eg $\dots \land
    (t' = t) \land (zone' = zone)$ in the guard of SV0. Shall we
    update the figure to include these or, rather, explain that the
    figure is cleaned-out for readability?}
%
\end{figure}

@@

The encoding of the interaction model is based on its representation
as a set of connectors. \noteSB{%
%
  A legitimate question is whether we actually need to do this,
  instead of listing explicitly the individual interactions, then
  associating a synchronisation vector to each one of them?  One of
  the factors is the encoding pNets$\rightarrow$SAT: is it better to
  have more or fewer SVs if the price is additional Boolean variables?
  The other factor might be the facility of maximal progress
  encoding\mdash TBC.  Traceability.  Anything else?\newline
  \hl{UPDATE: Maximal progress encoding requires this!}
%
} Indeed, as illustrated by the Failure Monitor architecture in
\fig{schema:ArchFailure:BIP}, each connector can define several
allowed interactions, depending on its hierarchical structure and the
use of synchrons and triggers.

\todoSB{Update?}\hl{In order to encode these interactions using only one synchronisation vector}, we use
the additional Boolean values associated to each port by the encoding
of coordinator components.  For example, observe that the three ports in 
the connector
{\NameTimer.\PortTick
  \trigsynch (\PortFail \trigsynch \NameCtrl.\PortFail)}
form a ``causality chain'': {\NameCtrl.\PortFail} can only
participate in the interaction if the dangling port {\PortFail}
participates, which in turn can only participate if
{\NameTimer.\PortTick} does so.  These dependencies can be rewritten
as Boolean implications $\NameCtrl.\PortFail \Rightarrow \PortFail$
and $\PortFail \Rightarrow \NameTimer.\PortTick$.
%
The conjunction of these two implications can be used as a guard for
the synchronisation vector encoding this connector.

@@

We obtain the
synchronisation vector SV0 shown in \fig{FailureTimer:pNet}, where $b_0$ and
$b_1$ are the Boolean values associated to the actions encoding the
ports {\PortFail} and {\NameCtrl.\PortFail}, $\alpha_0$ is a fresh
action name.  The guard $b_1 \Rightarrow b_0$ encodes the causal
relation between ports {\NameCtrl.\PortFail} and {\PortFail}.  Notice
that, in our encoding, all three ports are present in the
synchronisation vector.  \Fig{FailureTimer:pNet} shows
the four synchronisation vectors SV0\ndash SV3 corresponding to the
connectors in \fig{schema:ArchFailure:BIP} and an additional vector
SV4, synchronising the {\init} transitions of the two pLTSs.

The general case encoding relies on the causal semantics of the
algebra of BIP connectors \cite{BliSif10-causal-fmsd}.  Disregarding
the variables and data transfer, the Algebra of Connectors $\ac(P)$
\cite{BliSif07-acp-emsoft} provides a syntactic notation for the BIP
connectors.  The causal semantics of the connectors, given in terms of
the Algebra of Causal Interaction Trees $\ct(P)$, explicitates the
causal dependencies discussed above, through an encoding mapping
$\tau: \ac(P) \rightarrow \ct(P)$.  Another mapping $R: \ct(P)
\rightarrow \cru(P)$ encodes causal interaction trees into systems of
causal rules, which are Boolean implications similar to the ones in
the example above.  We briefly summarise the key definitions and
results in \app{algebras}.  The $\ac(P)$, $\ct(P)$ and $\cru(P)$
representations of the connectors in \fig{schema:ArchFailure:BIP} are
shown in \tab{connectors} (elements shown in red can be removed for
simplification as described in the example above).

@@

Below, we assume that, as in \fig{schema:ArchFailure:BIP}, the
interaction model is defined by a set of connectors, annotated with
Boolean guards and with update assignments.  In particular, we assume
that the guards and update assignments are well-defined for any
interaction allowed by the connector.  For example, the choice
$\NameCtrl.\PortFail\ ?\ \NameCtrl.\mathit{zone} : \topinterval$ in
the update assignement
\[
\NameTimer.\mathit{z} := \NameTimer.\mathit{z}
\cap \Big(
\bigl(
\NameCtrl.\PortFail\ ?\ \NameCtrl.\mathit{zone} : \topinterval
\bigr)
+ \NameTimer.\mathit{t} \Big)
\]
associated to the connector {\NameTimer.\PortTick \trigsynch
  (\PortFail \trigsynch \NameCtrl.\PortFail)} in
\fig{schema:ArchFailure:BIP} ensures that the assignment is
well-defined independently of whether {\NameCtrl.\PortFail}
participates or not.  Let us denote by $\gamma \subset \ac(P_A)
\times \guards{V_A} \times \assigns{V_A}$ the set of connectors in the
architecture $A$ and by $P_x$ the set of ports involved in the
connector $x \in \gamma$.  Then, \addSB{the interaction model defined by $\gamma$ is 
  $\Gamma = \setdef{(a,g,u)}{(x,g,u) \in \gamma, a \in \intsem{x}}$
  and the encoding of $\Gamma$ is} $\nopri[\Gamma] \bydef{=}
\setdef{\nopri[x,g,u]}{(x,g,u) \in \gamma}$, where $\nopri[x,g,u]$ is the synchronisation vector defined by
%
\begin{multline}
  \label{eq:nopri:connector}
  \nopri[x,g,u] \bydef{=}
  \Tuple{p\bigl(\export[A](p),{{\color{blue}\export[A]'(p),}}b_p\bigr)}^{p \in P_x}
  \rightarrow
  \alpha_p
  \\
  \left[
    \bigwedge R(\tau(x))\bigl[\nicefrac{b_p}{p}\bigr]
    {\color{blue}{}
    \land
    \bigwedge_{(x := e_x) \in u} (x' = e_x)
    \land
    \bigwedge_{x \in \export[A](x), x \not\in u} (x' = x)
    }
    \right]
  \,,
\end{multline}
\noteSB{Ought to group ports by components in
  $\Tuple{p\bigl(\export[A](p),\export[A]'(p),b_p\bigr)}^{p \in P_x}$...
  \newline
  Will probably restrict interactions to one port per component
  throughout the paper to simplify.
}
%
with $b_p$ a fresh Boolean variable, $\alpha_p$ a fresh name, $\tau :
\ac(P_A) \rightarrow \ct(P_A)$ and $R : \ct(P_A) \rightarrow
\cru(P_A)$ the two mappings defined in \app{transformations} and
illustrated in \tab{connectors}, $\bigl[\nicefrac{b_p}{p}\bigr]$ is
the substitution, which replaces, in the expression that preceeds it,
all occurrences of $p$ by $b_p$.

\begin{theorem}
  The open automaton $\semopen{\nopri[A,\partition]}$ corresponding to
  $\nopri[A,\partition]$ is
  isomorphic to the LTS $\semopen{\Gamma\bigl(\cC_A, (B_D)^{D \in
      \partition}\bigr)}$ (see \defn{comp:semantics}), where, for each
  $D \in \partition$, the component $B_D \bydef{=} \tuple{\{q\}, q,
    V_D, \val{0}{D}, D, \export[D], \goesto{}}$, with
  a fresh state $q$ and

%
  \begin{align*}
    V_D &= \bigcup_{p \in D} \export[A](p)
    \,,
    &\val{0}{D}(v) &= \bot, \text{ for all $v \in V_D$}
    \,,\\
    \goesto{} &= \bsetdef{(q, p, \true, \noop, q)}{p \in D}
    \,,
    &\export[D](p) &= \export[A](p), \text{ for all $p \in D$}
    \,.
  \end{align*}
%
\end{theorem}
%
\begin{proof}[Sketch of a proof]
  \noteSB{This theorem is very probably correct: the key question is
  whether isomorphism is, indeed, the relation to use. In absence of
  silent transitions, must be the case.}
  The theorem follows from the correctness of $\tau$ and $R$ shown in
  \cite{BliSif10-causal-fmsd}.
\end{proof}

\todoSB{This repeats things that were already said before.  Will reduce.}
Observe now that this encoding can be optimised to remove unnecessary
Boolean variables and loop transitions marked by \false.  For
instance, consider the ports shown in red in the second column of
\tab{connectors}.  All these ports only appear in the roots of the
corresponding causal interaction trees and, furthermore, each of these
trees only has one root (see \app{trees}).  In such cases, as in the
{\NameTimer.\PortTick \trigsynch (\PortFail \trigsynch
  \NameCtrl.\PortFail)} example discussed above, the Boolean variables
and the \false-marked loop transitions associated to these ports can
be removed.  Furthermore, the rules associated to these ports in the
corresponding systems of causal rules (see the rules in red in the
third column of \tab{connectors}) become tautological and can also be
removed from the corresponding guards in \eq{nopri:connector}.

@@

\todoSBin{Complete this section}
